Title

### 2014-01-22 paper/parts/conclusions.tex
notes in conclusion

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent, and that different definitions of communities reveal different relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network alone. We found that community structure differs across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific memberships, comemberships) scale.

We have also demonstrated that boundaries between communities represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without. We found this to be the case even when the communities were defined by a different criteria from the edge weights.

@@

Our work has introduced a novel use of transfer entropy for the detection of activity-based communities. In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users. Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}. In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.

@@

% Using concepts like centrality to determine influence 
% 	* These metrics are based solely on the structural network.
% 	* Your *activity* may be more important than your *topology* in determining
% 	  your influence.

Our findings have important implications to a common problem in social network analysis: identification of influential individuals. Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that a structural network is not sufficient to capture user interaction in online social media. Thus, a naive application of centrality measures to a structural network for influence detection may give rise to erroneous results. This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance. Moreover, weighted generalizations of these centralities might lead to better insights about who is actually influential in an online social network.

>>>>

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent [[Joshua:maybe reword this sentence to explicitly say what we mean by question-dependent", might be a little confusing]], and that different definitions of communities reveal different relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network alone. We found that community structure differs across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific memberships, comemberships) scale.

We have also demonstrated that boundaries between communities represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without. We found this to be the case even when the communities were defined by a different criteria from the edge weights. [[Wasn't this the opposite in the transfer entropy case? Maybe I am remembering wrong. If so maybe we can spend a few sentences explaining why this is so leading into the next paragraph]]

@@

[[This paragraph needs to be recrafted a bit. It just reads a little confusing]]Our work has introduced a novel use of transfer entropy for the detection of activity-based communities. In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users. Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}. In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.

@@

% Using concepts like centrality to determine influence 
% 	* These metrics are based solely on the structural network.
% 	* Your *activity* may be more important than your *topology* in determining
% 	  your influence.
[[While I agree with this next paragraph completely I am not sure we covered this topic enough to be the final paragraph of the conclussion or even in the conclusion. I need to think about this...]]
Our findings have important implications to a common problem in social network analysis: identification of influential individuals. Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that a structural network is not sufficient to capture user interaction in online social media. Thus, a naive application of centrality measures to a structural network for influence detection may give rise to erroneous results. This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance. Moreover, weighted generalizations of these centralities might lead to better insights about who is actually influential in an online social network.
